hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2024-11-26 inst/manuscript/paper.Rmd
workflow figure revisions

```{r echo=FALSE, eval=FALSE}
## THIS WONT WORK WITH PDF OUTPUT

graph <- 
  "digraph {
      # a 'graph' statement
      graph [overlap = false, label = 'hatchR workflow',labelloc = t, fontsize = 30]
      # label nodes
      node [fontsize = 20]
      import [label = 'import data', shape = circle, fillcolor = Beige]
      dates [label = 'check dates', shape = circle, fillcolor = Beige]
      plot1 [label = 'plot_check_data()' shape = rectangle]
      format [label = 'is data as\ndaily average?', shape = circle, fillcolor = Beige]
      plot2 [label = 'plot_check_data()' shape = rectangle]
      summarize [label = 'sumamrize_temp()',  shape = rectangle]
      continuous [label = 'check_continuous()', shape = rectangle]
      model [label = 'model type:\ncustom or included?', shape = circle, fillcolor = Beige]
      select [label = 'model_select()', shape = rectangle]
      fit [label = 'fit_model()', shape = rectangle]
      phenology [label = 'predict_phenology()', shape = rectangle]
      plot3 [label = 'plot_phenology()', shape = rectangle]
      # edge definitions with the node IDs
      edge [fontsize = 20]
      import -> dates
      dates -> dates [label = 'not dttm\nuse lubridate']
      dates-> plot1 [label = 'is dttm']
      plot1 -> format
      format -> summarize [label = 'multiple measures\nw/in a day']
      format -> model [label = 'mean daily average']
      summarize -> continuous -> plot2 -> model
      model -> select [label = 'hatchR built-in\nmodel']
      model -> fit [label = 'user custom data']
      {select, fit} -> phenology
      phenology -> plot3
    }
"

DiagrammeR::grViz(graph,
    width = 500
    )

>>>>

```{r echo = FALSE, out.height = '50%', fig.align = 'center'}
knitr::include_graphics("flowchart.png")
```
